3.3 OLS: OLS: Model Specification Strategies - R Practice

### 2019-10-29 static/r/15-r-practice-rmd.Rmd
Quick format tweak to practice 15 rmd

### Part E
Look at your regression table in question 10. What happened to the standard error on `Age`? Why (consider the formula for variation in $\hat{\beta_1})$
---

@@

### Part F
Calculate the Variance Inflation Factor (VIF) using the `car` package's `vif()` command.^[Run it on your multivariate regression object from Question 7.]

>>>>

### Part E

Look at your regression table in question 10. What happened to the standard error on `Age`? Why (consider the formula for variation in $\hat{\beta_1})$
---

@@

### Part F

Calculate the Variance Inflation Factor (VIF) using the `car` package's `vif()` command.^[Run it on your multivariate regression object from Question 7.]
